Implementation of Parallel Algorithms for ARIMA in Distributed Database Systems

### 2013-09-19 draft.tex
Minor changes to make vim and atp-vim plugin work together
Updates

\begin{abstract}
  MADlib is an open-source library for scalable in-database
  analytics. It provides data-parallel implementations of
  mathematical, statistical and machine-learning methods for
  structured and unstructured data. We impemented ARIMA in MADlib's
  framework. The algorithms for fitting ARIMA model to time series are
  intrinsically sequential, because any calculation for a specific
  time $t$ depends on the
  result from the calculation for $t-1$. This makes it difficult to
  parallelize the ARIMA model fitting. Our solution parallelizes the
  computation by splitting the data into $n$ chunks. Since the model
  fitting involves multiple iterations of computations. We use the
  results from previous iteration as the initial values for each
  chunk. Thus the computation for each chunk of data does not need to
  wait for the results from previous chunk. Another technique is used
  to improve the performance of the implementation, which
  redistributes the original data so that each chunk can be completely
  loaded into memory.
\end{abstract}

@@

% Introduce to MADlib, and implement ARIMA in MADLib

>>>>

\begin{abstract} MADlib is an open-source library for scalable in-database
  analytics. We impemented ARIMA in MADlib's framework. The algorithms for
  fitting ARIMA model to time series are intrinsically sequential, because any
  calculation for a specific time $t$ depends on the result from the
  calculation for $t-1$.  This makes it difficult to parallelize the ARIMA
  model fitting. Our solution parallelizes the computation by splitting the
  data into $n$ chunks. Since the model fitting involves multiple iterations of
  computations. We use the results from previous iteration as the initial
  values for each chunk. Thus the computation for each chunk of data does not
  need to wait for the results from previous chunk. Another technique is used
  to improve the performance of the implementation, which redistributes the
  original data so that each chunk can be completely loaded into memory.
  \end{abstract}

@@

% Introduce to MADlib, and implement ARIMA in MADLib
MADlib is an open source library for scalable in-database analytics. It is
created by the Predictive Analytics Team at Pivotal Inc. MADlib provides
data-parallel implementations of mathematical, statistical and machine-learning
methods for structured and unstructured data.
